---
title: "Rube This Cube: Self-Report Analysis"
author: "aiswary-a"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# Loading In: Packages & CSV
```{r, results = 'hide', warning = FALSE}

library(pacman)
pacman::p_load(tidyverse,
               PMCMRplus # for post-hoc Nemenyi test
               )

overlord <- read_csv(
  "C:/Users/aisro/Desktop/UNI/BSc CogSci - 3rd Sem/Perception and Action/EXAM_Rubiks/PA_RubeCube_Experiment.csv/PA_RubeCube_Experiment.csv"
)

df <- overlord[, c(2, 4, 5, 6, 7, 8, 9, 10, 11, 12)]
colnames(df) <- c(
  "condition",
  "id",
  "gender",
  "age",
  "1_confidence",
  "1_difficulty",
  "2_confidence",
  "2_difficulty",
  "3_confidence",
  "3_difficulty",
  "performance"
)

df <- df %>% 
  filter(id != "SR08")

```
## Restructuring Data for Plotting
```{r, warning = FALSE, message = FALSE}

df_long <- df %>%
  pivot_longer(
    cols = starts_with(c("1_", "2_", "3_")),
    names_to = c("time", "metric"),           
    names_pattern = "(\\d)_(.*)",             
    values_to = "score"
  )

df_summary <- df_long %>%
  group_by(condition, time, metric) %>%
  summarise(
    mean = mean(score, na.rm = TRUE),
    se = sd(score, na.rm = TRUE) / sqrt(n())
  )

```


## Plotting Self-Assessments over Time
```{r}

# confidence plot
plot_confidence <- ggplot(df_summary %>% filter(metric == "confidence"), aes(x = time, y = mean, color = condition, group = condition)) +
  geom_line() + 
  geom_point() +
#  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) + ## nicer to have when conditions have their own graphs, otherwise messy
  labs(x = "Time Point", y = "Average Confidence", color = "Condition") +
  theme_minimal() +
#  facet_wrap(~condition) + # to have 4 separate graphs
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_confidence

# difficulty plot
plot_difficulty <- ggplot(df_summary %>% filter(metric == "difficulty"), aes(x = time, y = mean, color = condition, group = condition)) +
  geom_line() + 
  geom_point() +
 # geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) + ## nicer to have when conditions have their own graphs, otherwise messy
  labs(x = "Time Point", y = "Average Perceived Difficulty", color = "Condition") +
  theme_minimal() +
#  facet_wrap(~condition) + # to have 4 separate graphs
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_difficulty

```
## Friedman Test (Non-Parametric ANOVA)
```{r}

# Friedman Test for Confidence
friedman_confidence <- friedman.test(
  score ~ time | id,
  data = df_long %>% filter(metric == "confidence")
)

# Friedman Test for Difficulty
friedman_difficulty <- friedman.test(
  score ~ time | id,
  data = df_long %>% filter(metric == "difficulty")
)

# Results!
#friedman_confidence
#friedman_difficulty

cat("\nFriedman Test Results for Confidence:\n")
cat("Chi-squared: ", friedman_confidence$statistic, "\n")
cat("Degrees of Freedom: ", friedman_confidence$parameter, "\n")
cat("p-value: ", friedman_confidence$p.value, "\n")
if (friedman_confidence$p.value < 0.05) {
  cat("Interpretation: There is a significant difference in confidence across the time points.\n")
} else {
  cat("Interpretation: There is no significant difference in confidence across the time points.\n")
}

cat("\nFriedman Test Results for Difficulty:\n")
cat("Chi-squared: ", friedman_difficulty$statistic, "\n")
cat("Degrees of Freedom: ", friedman_difficulty$parameter, "\n")
cat("p-value: ", friedman_difficulty$p.value, "\n")
if (friedman_difficulty$p.value < 0.05) {
  cat("Interpretation: There is a significant difference in difficulty across the time points.\n")
} else {
  cat("Interpretation: There is no significant difference in difficulty across the time points.\n")
}

```
## Post-Hoc Testing
```{r}

# Post-Hoc Nemenyi Test

p_load(PMCMRplus)

# Post-Hoc Nemeyi Test for Confidence
posthocNemenyi_confidence <- PMCMRplus::frdAllPairsNemenyiTest(
  score ~ time | id, data = df_long %>% filter(metric == "confidence")
  )

# Post-Hoc Nemeyi Test for Difficulty
posthocNemenyi_difficulty <- PMCMRplus::frdAllPairsNemenyiTest(
  score ~ time | id, data = df_long %>% filter(metric == "difficulty")
  )

# Results!
posthocNemenyi_confidence
posthocNemenyi_difficulty

```
(where Group 1 = first time point, Group 2 = second time point, Group 3 = third time point)

* For confidence, a significant difference was found between groups 1 and 2 (p = 0.033). No other pairwise differences were significant.

* For difficulty, a significant difference was found between groups 1 and 3 (p = 0.046. No other pairwise differences were significant.



